---
title: "WTG_model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{WTG_model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wmdata)
library(tidyverse)
library(ggplot2)
data(Ws)
```

Consider the wind speed, $\nu_r$, recorded at a reference height, $h_r$, and the proposed wind turbine with hub height, $h_h$, then the wind speed at the hub height, $\nu_h$, is given by
\[\nu_h = \nu_r\left(\frac{h_h}{h_r}\right)^\gamma\,,\]
where $\gamma \approx \frac{1}{7}$ for open land. 

Wind turbines start to produce power when the wind speed is greater than the cut-in speed, $\nu_{ci}$, reach their maximum power output when the wind speed is greater than the rated wind speed, $\nu_r$, and stop producing power for high wind speed greater than the cut_out speed, $\nu_{co}$. The power output of a wind turbine is therefore a piecewise function given by
\[P = \begin{cases} P_r \left(\frac{\nu_h^3 - \nu_{ci}^3}{\nu_r^3-\nu_{ci}^3}\right) & \nu_{ci}\le \nu \le \nu_r\,,\\
P_r & \nu_r < \nu \le \nu_{co}\,, \\
0 & \text{otherwise}\,,
\end{cases}\]
where $P_r$ is the rated power of the turbine.

Consider the following parameters for a wind turbine:
```{r}
cut_in = 4
cut_out = 25
rated_speed = 13
rated_power = 4.2
```

These parameters produce the following power curve for the wind turbine.

```{r}
data.frame(speed = seq(0,30,by = 0.1)) %>%
  dplyr::mutate(power = WTG_model(speed,cut_in,cut_out,rated_speed,rated_power))%>%
  ggplot(aes(x = speed,y=power)) +
  geom_line()
```

